A possibilistic valid-time model

### 2011-11-17 ipmu2012/preliminaries.tex
Adaptation of the fuzzy interval and fuzzy number part. Let me know if you don't agree! I will now work on the part on interval evaluation by ill-known constraints.

When a possibilistic variable is defined on the powerset $\Pow(R)$ of some universe $R$, the unique value the variable takes will be a crisp set. In this case, the exact set is off course (partially) unknown, but the available knowledge is given in the form of a possibility distribution on the powerset $\Pow(R)$. This exact value (a crisp set) the variable takes, is now called an \emph{ill-known set}\cite{Dubois88b}.

In this work, an ill-known set will be defined via its start and end point, which will be ill-known values. The correspondences and transitions between these two representations are part of the authors current research.

@@

\subsection{\label{subsec:fuzzy-numbers}Fuzzy numbers and fuzzy intervals}
Dubois and Prade~\cite{Dubois1983} proposed the following definition of \emph{fuzzy interval}.
\begin{definition}
A fuzzy interval is a fuzzy set $M$ on the set of real numbers $\mathbb{R}$ such that:
\begin{eqnarray}
\forall (u,v)\in\mathbb{R}^2:&\\
\nonumber
\forall w \in [u,v]:&\mu_M(w) \geq\min(\mu_M(u),\mu_M(v))  \\
\exists m \in \mathbb{R}:& \mu_M(m)=1 
\end{eqnarray}
\end{definition}
If $m$ is unique, then $M$ is referred to as a \emph{fuzzy number}, instead of a \emph{fuzzy interval}. In other words, if the core of a fuzzy interval is a singleton, it can be seen as a fuzzy number. In their work, Dubois and Prade propose four different functions (two possibility and two necessity functions) to asses the position of a fuzzy number N relative to  a fuzzy number M taken as a reference.

The most convenient representation for the membership function of a fuzzy number is a triangular function. The membership function $\mu_M$ for the fuzzy set $M$ has also the properties of convexity and normalization. Three values represent a triangular function (see Figure~\ref{fig:triangular}):
\begin{itemize}
\item
$D$ is the singleton value in the core of $\mu_M(x)$.
\item
$D-a$ is the lower value in the support of $\mu_M(x)$. 
\item
$D+b$ is the upper value in the support of $\mu_M(x)$.
\end{itemize}
Note that the values $a$ and $b$ are values in the underlying ordered domain. E.g. $(a,b) \in \mathbb{R}^2$. The notation for a triangular function adopted here is $[D,a,b]$.
\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.4]{graphs/triangular.eps}
  \caption{Triangular function.}
  \label{fig:triangular}
\end{figure}

The most simple representation for the membership function of a fuzzy interval is a trapezoidal function. This membership function $\mu_T$ for the fuzzy interval $T$ is convex and normalized. Four values represent a trapezoidal membership function (figure  \ref{fig:trapezoidal}): $\left[\alpha,\ \beta,\ \gamma,\ \delta\right]$. The membership function is given by:

\begin{align}
\mu_T(x)
\begin{cases}
1 & \mbox{ if } x \in [\beta,\gamma] \\
0 & \mbox{ if } x > \delta \vee x < \alpha \\
\frac{x-\alpha}{\beta - \alpha} & \mbox{ if } x \in [\alpha,\beta[ \\
\frac{\delta -x}{\delta - \gamma} & \mbox{ if } x \in ]\gamma,\delta] \\
\end{cases}
\end{align}

\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.4]{graphs/trapezoidalDistribution.eps}
  \caption{Trapezoidal distribution.}
  \label{fig:trapezoidal}
\end{figure}

\subsubsection{Set evaluation by ill-known constraints}

>>>>

When a possibilistic variable is defined on the powerset $\Pow(R)$ of some universe $R$, the unique value the variable takes will be a crisp set. In this case, the exact set is off course (partially) unknown, but the available knowledge is given in the form of a possibility distribution on the powerset $\Pow(R)$, which describes the possibility of each crisp subset of $R$ to be the value the variable takes. This exact value (a crisp set) the variable takes, is now called an \emph{ill-known set}\cite{Dubois88b}.

In this work, an ill-known set will be defined and represented via its start and end point, which will be ill-known values. The correspondences and transitions between these two representations are part of the authors current research.

@@

\subsection{\label{subsec:fuzzy-numbers}Fuzzy numbers and fuzzy intervals}
Among others, Dubois and Prade~\cite{Dubois1983} use the following definition of a \emph{fuzzy interval}.
\begin{definition}
A fuzzy interval is a fuzzy set $M$, defined by a membership function $\mu_{M}$, on the set of real numbers $\mathbb{R}$ such that:
\begin{eqnarray}
\mu_{M} : & \!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\! \mathbb{R} \rightarrow \left[0,1\right] \nonumber \\ 
\forall (u,v)\in\mathbb{R}^2: \forall w \in [u,v]:&\mu_M(w) \geq\min(\mu_M(u),\mu_M(v))  \\
\exists m \in \mathbb{R} : & \!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\! \mu_M(m)=1 
\end{eqnarray}
\end{definition}
If this modal value $m$ is unique, then $M$ is referred to as a \emph{fuzzy number}, instead of a \emph{fuzzy interval}. In other words, if the core of a fuzzy interval is a singleton, it is referred to as a fuzzy number.

A simple form of the membership function of a fuzzy interval is a trapezoidal function. It can be shown that such a membership function $\mu_T$ for a fuzzy interval $T$ is convex and normalized. A visualization is given in figure \ref{fig:trapezoidal}. Four reel values, denoted $\alpha$, $\beta$, $\gamma$ and $\delta$ and chosen as in figure \ref{fig:trapezoidal}, suffice to represent a trapezoidal membership function of a fuzzy interval. In this work, a fuzzy interval defined as such will be noted as $\left[\alpha, \beta, \gamma, \delta\right]$. The corresponding membership function definition for this $\mu_T$ is then given by:

\begin{align}
\mu_T : & \quad \mathbb{R} \rightarrow \left[0,1\right] \\
 : & \quad x \rightarrow
\begin{cases}
1 & \mbox{ if } x \in [\beta,\gamma] \\
0 & \mbox{ if } x > \delta \vee x < \alpha \\
\frac{x-\alpha}{\beta - \alpha} & \mbox{ if } x \in [\alpha,\beta[ \\
\frac{\delta -x}{\delta - \gamma} & \mbox{ if } x \in ]\gamma,\delta] \\
\end{cases}
\end{align}

\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.4]{graphs/trapezoidalDistribution.eps}
  \caption{Trapezoidal membership function}
  \label{fig:trapezoidal}
\end{figure}

The most convenient form of the membership function of a fuzzy number is a triangular function. It can be shown that such a membership function $\mu_M$ for a fuzzy number $M$ is convex and normalized. A visualization is given in figure \ref{fig:triangular}. Three reel values, denoted $a$, $b$ and $D$, suffice to represent a triangular membership function of a fuzzy number.
\begin{itemize}
\item
$D$ denotes the single value in the core of $M$
\item
$D-a$ is then $\inf \{u \in \mathbb{R} : \mu_{M}(u) > 0\}$
\item
$D+b$ is then $\sup \{u \in \mathbb{R} : \mu_{M}(u) > 0\}$
\end{itemize}
In this work, a fuzzy number defined as such will be noted as $\left[D, a, b \right]$.
\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.4]{graphs/triangular.eps}
  \caption{Triangular membership function.}
  \label{fig:triangular}
\end{figure}

%\subsubsection{Set evaluation by ill-known constraints}
